---
title: "Final assingment BDAwR"
author: "Lino Zurmühl"
date: "8 9 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Article review "Are Social Bots on Twitter Political Actors? Emoirical Evidence from a UkrainianSocial Botnet" Hegelich/Janetzko 2016

originating question: Are Social bots Political actors?
central question: has the Ukrainian Social Botnet an political agenda? Which kind of behavoir can be identified?
specifying questions: what behaviors does the botnet have? how can these behaviors be interpreted? 

In their article from 2016 Hegelich and Janetzko asked themselves the question: are social bots on Twitter Political Actors? To answer this question they picked an exemplary botnet that was posting about the Ukrainian/Russian conflict. The authors collected the data via the twitter hashtag "#Ukraine" and with this dataset tried to find a political agenda behind the, in the dataset emerging, Ukrainian social botnet. Furthermore they posted the question of what different behaviors of the botnet can be identified. 


```{r}
install.packages("rvest")
install.packages("tidyverse")
install.packages("rtweet")
install.packages("magrittr")
library(rvest)
library(rtweet)
library(tidyverse)
library(magrittr)
data -> read_csv("TakeHomeFinal\timelines.csv")
glimpse ()
```

